%-------------------------
% FAANG-Style ATS Resume — Jayant Kumar
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{microtype}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting: caps, bold, ruled
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule\vspace{-4pt}]

\pdfgentounicode=1

%--------------------------
% Custom Commands
%--------------------------

\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small #1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge \scshape Jayant Kumar} \\[3pt]
  \small
  \raisebox{-0.1\height}{\faPhone}\ +91-87085-48651 \enspace$|$\enspace
  \href{mailto:Jayantgahlawat@gmail.com}{\raisebox{-0.15\height}{\faEnvelope}\ \underline{Jayantgahlawat@gmail.com}} \enspace$|$\enspace
  \href{https://linkedin.com/in/jayant-gahlawat-07980a32a}{\raisebox{-0.15\height}{\faLinkedin}\ \underline{linkedin.com/in/jayant-gahlawat}} \enspace$|$\enspace
  \href{https://github.com/Drifting-Moon}{\raisebox{-0.15\height}{\faGithub}\ \underline{github.com/Drifting-Moon}}
\end{center}
\vspace{-10pt}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Manipal University Jaipur}{Aug 2024 -- May 2028}
    {B.Tech in Computer Science and Engineering \textnormal{--- CGPA: \textbf{8.98 / 10.0}}}{Jaipur, Rajasthan}
\resumeSubHeadingListEnd
\vspace{-4pt}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt]
  \small{
    \item \textbf{Languages:} C,C++,JavaScript, TypeScript, Python, Java, SQL, HTML, CSS
    \item \textbf{Frameworks \& Libraries:} React 18, Tailwind CSS v4, Vite, lightweight-charts
    \item \textbf{Tools \& Platforms:} Git, GitHub, VS Code, Linux
    \item \textbf{Relevant Coursework:} Data Structures \& Algorithms, OOP, Database Management Systems, Operating Systems
  }
\end{itemize}


%-----------PROJECTS-----------
\section{Projects}
\vspace{-4pt}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{CommunityPulse --- AI Crisis Intelligence Platform} \enspace
   \emph{Gemini 2.0, Python, React, PWA} \enspace
    \href{https://github.com/krish230506-png/CommunityPulse}{{\small\faGithub} \underline{GitHub}}}{2026}
\resumeItemListStart
  \resumeItem{Built an AI-native disaster response platform for Google Solution Challenge 2026 using a Gemini 2.0 Flash agentic pipeline to process multimodal inputs (voice, images, text) into a real-time crisis map.}
  \resumeItem{Reduced dispatch latency from 45+ min to under 120 sec via Haversine geofencing; applied vector embeddings to deduplicate reports into prioritized Crisis Events (0--100 score).}
  \resumeItem{Architected an Offline-First PWA with 2G/3G background sync and 6+ Indian language support for operability in connectivity-dead disaster zones.}
\resumeItemListEnd
\vspace{-10pt}

\resumeProjectHeading
  {\textbf{Quantis --- Backtesting \& Portfolio Engine} \enspace
   \emph{JavaScript, Python, React, Tailwind CSS v4} \enspace
   \href{https://github.com/Drifting-Moon/Quantis}{{\small\faGithub} \underline{GitHub}}}{2025}
\resumeItemListStart
  \resumeItem{Engineered a full-stack financial backtesting platform simulating investment strategies against historical market data with live ``what-if'' scenario visualization.}
  \resumeItem{Authored a custom XIRR engine in Python for time-weighted returns on irregular cash flows; integrated Yahoo Finance API and CSV upload for multi-source portfolio construction.}
  \resumeItem{Built a ``Step Strategy'' engine automating SIP simulations with click-to-invest interactions on \texttt{lightweight-charts} financial charts.}
\resumeItemListEnd
\vspace{-10pt}

\resumeProjectHeading
  {\textbf{Canvas --- Interactive Sticky-Note Board} \enspace
   \emph{React 18, TypeScript, Vite} \enspace
   \href{https://github.com/Drifting-Moon/Canvas-Tree}{{\small\faGithub} \underline{GitHub}}}{2025}
\resumeItemListStart
  \resumeItem{Built a minimalist sticky-note web app with drag-and-drop, per-note resizing, dynamic color assignment, and \texttt{localStorage} persistence --- structured with React 18, TypeScript, and Vite.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}


%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, itemsep=4pt]
  \small{
    \item \textbf{Design and Analysis of Algorithms} \textnormal{--- NPTEL, IIT Madras} \hfill \textit{Jan -- Mar 2026}\\[1pt]
    \textnormal{8-week course covering divide \& conquer, greedy algorithms, dynamic programming, and complexity analysis.}

    \item \textbf{Generative AI: Introduction and Applications} \textnormal{--- IBM, Coursera} \hfill \textit{Feb 2026}\\[1pt]
    \textnormal{Foundations of generative AI, large language models, and real-world AI application design.}

    \item \textbf{Data Structures and Algorithms using Java} \textnormal{--- NPTEL, IIT Kharagpur} \hfill \textit{Jul -- Oct 2025}\\[1pt]
    \textnormal{12-week course covering sorting, searching, trees, graphs, and dynamic programming in Java.}
  }
\end{itemize}
\vspace{-8pt}


%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt]
  \small{
    \item \textbf{Competitive Programming:} Solved \textbf{125+ problems} on
    \href{https://leetcode.com/u/Red_Daoist/}{\underline{LeetCode (Red\_Daoist)}} and
    \href{https://www.geeksforgeeks.org/profile/jayantga25gi}{\underline{GeeksforGeeks (jayantga25gi)}} ---
    including \textbf{53 Medium} and \textbf{7 Hard} --- spanning Arrays, Binary Search, HashMaps \& Sets,
    Two Pointers, Sorting, and Divide \& Conquer.

    \item \textbf{Dean's List --- Semester 2:} Recognized among top academic performers at Manipal University Jaipur for the batch of 2028.
  }
\item \textbf{Google Solution Challenge 2026:} Built and deployed \textit{CommunityPulse}, an AI-native disaster response platform using a Gemini 2.0 Flash agentic pipeline --- reducing volunteer dispatch latency from 45+ minutes to under 120 seconds.

\end{itemize}


\end{document}
